### 2019-06-03 reports/thesis/chapters/2_dataCollection.tex
Writing data collection chapter

@@

\begin{figure}
  \centering
  \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
      \includegraphics[width=\textwidth]{../figures/data/AbsNoFilterDeg30.eps}
      \caption{Projection of sample at \SI{44}{\watt}}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
      \includegraphics[width=\textwidth]{../figures/data/AbsNoFilterDeg30_sim.eps}
      \caption{Simulation of sample at \SI{44}{\watt}}
    \end{subfigure}
  }
  \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
      \includegraphics[width=\textwidth]{../figures/data/AbsNoFilter_calibration1.eps}
      \caption{Projection at \SI{0}{\watt}}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
      \includegraphics[width=\textwidth]{../figures/data/AbsNoFilter_calibration5.eps}
      \caption{Projection at \SI{44}{\watt}}
    \end{subfigure}
  }
  \caption{Projections obtained; note the colour scale may vary.}
  \label{fig:data_AbsNoFilter}
\end{figure}

>>>>

An experiment was conducted where a test sample was additively manufactured with purposely designed voids. The objective is to see if the voids can be detected using a single projection. This was done by comparing a projection of the test sample with the simulation of that projection as if the voids were not there. The simulated projections were produced by software called \emph{aRTist} \citep{bellon2007artist, jaenisch2008artist, bellon2012radiographic}. It can simulate projections of the test sample given the specifications of the CT apparatus, such as the x-ray source and the x-ray detector, and the CAD of the test sample \citep{bellon2011simulation, deresch2012simulating}.

\cite{brierley2018optimized} did something similar by comparing a projection of the test sample, with no voids, with a simulation of that projection with voids added in the CAD. The experiment presented here is the other side of the coin, putting voids in the physical test sample rather than in the simulated projection. This makes the experiment more realistic by attempting to detect real voids. Being able to detect voids in projection space suggest quality control can be done in projection space, rather than reconstruction space, to speed up the quality control procedure.

This chapter describes the apparatus used to manufacture the test sample and obtaining the projections. There is also a discussion, at the end of the chapter, on shading correction which was used to remove detector panel and x-ray spot effects from the projections.

Many figures presented here were given by engineers in relation to the experiment or by the manufacturer. Figures with no error bars were rounded to an appropriate number of significant figures.

\section{Apparatus}

The test object is a cuboid (\SI{40.0}{\milli\metre} $\times$ \SI{40.0}{\milli\metre} $\times$ \SI{60.0}{\milli\metre}) with voids, the CAD shown in Figure \ref{fig:inference_testObject}. The voids were of diameters \SI{2.4}{\milli\metre}, \SI{1.2}{\milli\metre}, \SI{0.6}{\milli\metre} and \SI{0.3}{\milli\metre}. 6 voids for each diameter were designed in the CAD. Voids with diameters \SI{2.4}{\milli\metre} and \SI{0.6}{\milli\metre} were regularly arranged, otherwise they were arranged irregularly.

\begin{figure}
  \centering
  \includegraphics[width=0.4\textwidth]{../figures/inference/TestObject.png}
  \caption{CAD of the test object; the scale shown is approximate.}
  \label{fig:inference_testObject}
\end{figure}

The \emph{Fortus 400mc (Stratasys, US)} was used to manufacture the test object made of plastic (acrylonitrile butadiene styrene or ABS). The precision of the manufacturing was in the order of $\pm\SI{0.1}{\milli\metre}$ \citep{hanseen2013fortus}. Another test object was manufactured made from titanium (Ti-6Al-4V)

X-ray projections were obtained using the \emph{Nikon XT H LC 225/320} x-ray CT scanner (\emph{Nikon Metrology, UK}) together with a \emph{Perkin Elmer XRD 1621 (Perkin Elmer, US)} detector. The target material in the x-ray source is tungsten. The sensor in the detector is made up of 2 rows and 16 columns of panels. The sensor has dimensions of $\SI{409.6}{\milli\metre}\times\SI{409.6}{\milli\metre}$ with produced a projection of $\SI{2048}{\pixel}\times\SI{2048}{\pixel}$ in size \citep{perkinelmer2006xrd}. Therefore the scale of each pixel is $\SI{200.0}{\micro\metre\per\pixel}$. The projections were cropped to $\SI{2000}{\pixel}\times\SI{2000}{\pixel}$ to remove boundary effects. The gain and offset were adjusted by the engineers to produce a projection with good contrast, each pixel then has a grey value in units of analogue to digital units (\SI{}{\adu}).

Greyscale projections were taken in addition to the projection of the test object. These are projections with nothing to scan at different powers used in the x-ray tube. The power was varied by fixing the potential difference and varying the current. The greyscale projections were used for calibration such as shading correction.

Replicate projections of the test object and greyscale projections were obtained by repeating the scan. These replicated projections were used to study the noise observed in the projections.

Filters used to tackle beam hardening were used such as \SI{0.350}{\milli\metre} of copper and \SI{2.000}{\milli\metre} of tin.

\section{Datasets}

3 datasets were collected and named \texttt{AbsNoFilter}, \texttt{AbsFilter} and \texttt{TiFilter}. Projections of the ABS test object were taken in \texttt{AbsNoFilter} and \texttt{AbsFilter}, the titanium test object was used in \texttt{TiFilter}. 2 angular projections were taken for all datasets as well as greyscale projections. To investigate the effects of beam hardening, no x-ray filter was used in \texttt{AbsNoFilter}, a filter was used in \texttt{AbsFilter}.

The properties of each dataset is shown in Table \ref{table:data_dataset}. Properties include the x-ray tube, the XCT apparatus and what powers were used in the greyscale projections. A sample of the obtained, simulated and greyscale projections for the datasets \texttt{AbsNoFilter}, \texttt{AbsFilter} and \texttt{TiFilter} are shown in Figures \ref{fig:data_AbsNoFilter}, \ref{fig:data_AbsFilter} and \ref{fig:data_TiFilter} respectively.

\begin{sidewaystable}
\centering
\begin{tabular}{l|lll}
                                                       & \multicolumn{3}{c}{Dataset name}                                                \\
                                                       & \texttt{AbsNoFilter} & \texttt{AbsFilter}             & \texttt{TiFilter}        \\ \hline
potential difference (\SI{}{\kilo\volt})               & 80                   & 80                             & 190                      \\
power (\SI{}{\watt})                                   & 36                   & 20                             & 19.95                    \\
filter                                                 & no filter            & \SI{0.35}{\milli\metre} copper & \SI{3}{\milli\metre} tin \\
time exposure (\SI{}{\milli\second})                   & 708                  & 500                            & 1415                     \\
distance from source to object (\SI{}{\milli\metre})   & 217                  & 168                            & 86                       \\
distance from source to detector (\SI{}{\milli\metre}) & 1178                 & 876                            & 875                      \\
number of replications                                 & 100                  & 20                             & 20                       \\ \hline
powers used for greyscale projections (\SI{}{\watt})   & 0                    & 0                              & 0                        \\
\multicolumn{1}{c|}{\vdots}                            & 10.08                & 4.96                           & 10.07                    \\
\multicolumn{1}{c|}{\vdots}                            & 18.08                & 10                             & 19.95                    \\
\multicolumn{1}{c|}{\vdots}                            & 28                   & 15.04                          &                          \\
\multicolumn{1}{c|}{\vdots}                            & 36                   & 20                             &                          \\
number of replications                                 & 20                   & 20                             & 20                      
\end{tabular}
\caption{Properties of the 3 datasets obtained for the experiment.}
\label{table:data_dataset}
\end{sidewaystable}

\begin{figure}[p]
  \centering
  \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
      \includegraphics[width=\textwidth]{../figures/data/AbsNoFilterDeg30.eps}
      \caption{Projection of sample at \SI{36}{\watt}}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
      \includegraphics[width=\textwidth]{../figures/data/AbsNoFilterDeg30_sim.eps}
      \caption{Simulation of sample at \SI{36}{\watt}}
    \end{subfigure}
  }
  \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
      \includegraphics[width=\textwidth]{../figures/data/AbsNoFilter_calibration1.eps}
      \caption{Projection at \SI{0}{\watt}}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
      \includegraphics[width=\textwidth]{../figures/data/AbsNoFilter_calibration5.eps}
      \caption{Projection at \SI{36}{\watt}}
    \end{subfigure}
  }
  \caption{\texttt{AbsNoFilter} projections obtained; note the colour scale may vary.}
  \label{fig:data_AbsNoFilter}
\end{figure}

\begin{figure}[p]
  \centering
  \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
      \includegraphics[width=\textwidth]{../figures/data/AbsFilterDeg30.eps}
      \caption{Projection of sample at \SI{20}{\watt}}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
      \includegraphics[width=\textwidth]{../figures/data/AbsFilterDeg30_sim.eps}
      \caption{Simulation of sample at \SI{20}{\watt}}
    \end{subfigure}
  }
  \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
      \includegraphics[width=\textwidth]{../figures/data/AbsFilter_calibration1.eps}
      \caption{Projection at \SI{0}{\watt}}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
      \includegraphics[width=\textwidth]{../figures/data/AbsFilter_calibration5.eps}
      \caption{Projection at \SI{20}{\watt}}
    \end{subfigure}
  }
  \caption{\texttt{AbsFilter} projections obtained; note the colour scale may vary.}
  \label{fig:data_AbsFilter}
\end{figure}

\begin{figure}[p]
  \centering
  \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
      \includegraphics[width=\textwidth]{../figures/data/TiFilterDeg30.eps}
      \caption{Projection of sample at \SI{20}{\watt}}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
      \includegraphics[width=\textwidth]{../figures/data/TiFilterDeg30_sim.eps}
      \caption{Simulation of sample at \SI{20}{\watt}}
    \end{subfigure}
  }
  \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
      \includegraphics[width=\textwidth]{../figures/data/TiFilter_calibration1.eps}
      \caption{Projection at \SI{0}{\watt}}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
      \includegraphics[width=\textwidth]{../figures/data/TiFilter_calibration3.eps}
      \caption{Projection at \SI{20}{\watt}}
    \end{subfigure}
  }
  \caption{\texttt{TiFilter} Projections obtained; note the colour scale may vary.}
  \label{fig:data_TiFilter}
\end{figure}

The projections do indeed show the test sample, however, with panel and spot effects. The structure of the 32 panels are predominate in the black image in particular, this was observed by \cite{yang2009evaluation} as well. This is concerning because systematic errors could be caused as a result of the panel effects in the black image when presented only with background radiation. The x-ray spot can be observed, in particular in the white image, and is the result of using a cone beam. \cite{kueh2016modelling} studied the x-ray spot by fitting a mixture of a Gaussian spot and an uniform spot onto the x-ray spot.

\section{Shading Correction}

Shading correction, also known as flat field correction, aims to eliminate any spatial variation in sensitivity of the projections such as panel and spot effects. Shading correction is typically done using the greyscale projections and how the pixels respond to different powers. For example the black and white images can be used to correct the projection using
\begin{equation}
U_{x,y} = \dfrac{N_{x,y}-\text{black}_{x,y}}{\text{white}_{x,y}-\text{black}_{x,y}}\times B+A
\end{equation}
where $N_{x,y}$ is the obtained projection, $U_{x,y}$ is the shading corrected projection and $A$ and $B$ are some user defined constants \citep{young2000shading, munzenmayer2003enhancing}. This can be extended to include more greyscale projections by using the fact that the grey value respond linearly to the power of the x-ray source \citep{seibert1998flat}. More generally, shading correction can be expressed as
\begin{equation}
U_{x,y} = N_{x,y} \beta_{x,y} + \alpha_{x,y}
\end{equation}
where $\alpha_{x,y}$ and $\beta_{x,y}$ are some spatially varying functions \citep{munzenmayer2003enhancing}. However there is an argument that this model has limitations because $\alpha_{x,y}$ and $\beta_{x,y}$ depends on the energy of each photon, thus beam hardening could cause inaccuracies in shading correction \citep{davidson2003limitations}.

Other methods include minimising the entropy of the projection while constraining $\alpha_{x,y}$ and $\beta_{x,y}$ to some parametric function \citep{likar2000retrospective}. There is also a method which uses a low pass filter to remove low spatial frequencies from the projections \citep{young2000shading, munzenmayer2003enhancing}.

In this section, the shading correction in \cite{seibert1998flat} is presented in a form without any user defined constants. The shading correction was then experimented to investigate its performance when shading correcting greyvalue projections.

\subsection{Proposed Shading Correction}

Let $N_{x,y}(P)$ be the grey value of pixel $(x,y)$ after being exposed to x-rays of power $P$ for some fixed exposure time. The power can be varied at the x-ray source when obtaining the greyscale projections or via attenuation assuming no beam hardening. Let $U_{x,y}(P)$ be the shading-free pixel at $(x,y)$. Assume that
\begin{equation}
U_{x,y}(P) = N_{x,y}(P)\beta_{x,y}+\alpha_{x,y}
\end{equation}
where $\beta_{x,y}$ and $\alpha_{x,y}$ is some constant which varies spatially. Suppose when

\subsection{ANOVA}

@@
